Dissecting Happiness: A Cross-National Analysis of Income Inequality and Its Impact

### 2024-04-19 paper/paper.qmd
adding a title and last bits

---
title: "My title"
author: 
  - Carl Fernandes
thanks: "Code and data are available at: https://github.com/Carl-1506/Happiness-and-inequality.git"
date: today
date-format: long
abstract: "This study explores the connection between income inequality and national hapiness, questioning the impact of the Gini index. By examining cross-sectional data we find that income inequality has a limited direct effect on happiness. It is evident that factors like the quality of institutions and levels of development as measured by the Democracy Index and the Inequality adjusted Human Development Index (IHDI) have a more significant impact on shaping happiness. Our results indicate that focusing solely on income inequality doesn't provide a complete understanding. Instead a wider range of indicators are. This research contributes to the conversation on disparity and satisfaction by emphasizing the importance of using multifaceted approaches in happiness research and policy development."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Dissecting Happiness: A Cross-National Analysis of Income Inequality and Its Impact"
author: 
  - Carl Fernandes
thanks: "Code and data are available at: https://github.com/Carl-1506/Happiness-and-inequality.git"
date: today
date-format: long
abstract: "This study explores the connection between income inequality and national hapiness, questioning the impact of the Gini index. By examining cross-sectional data we find that income inequality has a limited direct effect on happiness. It is evident that factors like the quality of institutions and levels of development as measured by the Democracy Index and the Inequality adjusted Human Development Index (IHDI) have a more significant impact on shaping happiness. Our results indicate that focusing solely on income inequality doesn't provide a complete understanding. Instead a wider range of indicators are. This research contributes to the conversation on disparity and satisfaction by emphasizing the importance of using multifaceted approaches in happiness research and policy development."
format: pdf
number-sections: true
bibliography: references.bib
---
